---
title: "hw2"
author: "Hanfei Dong"
date: "2024-02-08"
output: html_document
---

```{r warning=FALSE, message=FALSE}

library(tidyverse)
library(ggplot2)

```

``` {r}
xtabs(~ brfss22$ADDEPEV3 + brfss22$SEXVAR)
```

``` {r}
prop.table(table(brfss22$ADDEPEV3, brfss22$SEXVAR))
```

``` {r}
NN <- length(brfss22$ADDEPEV3)
set.seed(12345)
restrict_1 <- (runif(NN) < 0.1)
summary(restrict_1)
```

``` {r}
brfss_small <- subset(brfss22, restrict_1)
```

``` {r}
ggplot(brfss_small, aes(x = EDUCA, fill = ADDEPEV3)) + geom_bar(position = "fill") + scale_fill_viridis_d()
```

``` {r}
ggplot(brfss_small, aes(x = ADDEPEV3, fill = EDUCA)) + geom_bar()
```


``` {r}
ggplot(brfss_small, aes(x = X_AGEG5YR, fill = ADDEPEV3)) + geom_bar(position = "fill") + scale_fill_viridis_d()
```

``` {r}
ggplot(brfss_small, aes(x = ADDEPEV3, fill = X_AGEG5YR)) + geom_bar()
```

The data here on the age of depressed people as well as their education is interesting, and I've visualized it as a ratio to make it easier to see.
However, since the population base for each age group as well as education is inherently uncontrolled in brfss_small's sample, more rigorous experiments using this raw data or other studies will have to be consulted if one wants to study the correlation between age, education and depression.
