---
title: "Lab 6"
author: "Hanfei Dong"
date: "2024-04-05"
output: html_document
---

``` {r}
load("D:/psy StatMethod/BRFSS2022_rev.RData")
``` 

``` {r}
library(ggplot2)
library(tidyverse)
``` 

```{r}
brfss22$Age_midpt <- fct_recode(brfss22$X_AGEG5YR, "21" = "Age 18 to 24",
                                      "27" = "Age 25 to 29", "32" = "Age 30 to 34",
                                      "37" = "Age 35 to 39", "42" = "Age 40 to 44",
                                      "47" = "Age 45 to 49", "52" = "Age 50 to 54",
                                      "57" = "Age 55 to 59", "62" = "Age 60 to 64",
                                      "67" = "Age 65 to 69", "72" = "Age 70 to 74",
                                      "77" = "Age 75 to 79", "82" = "Age 80 or older",
                                      NULL = "Dont know/Refused/Missing")
brfss22$Age_midpt <- as.numeric(levels(brfss22$Age_midpt))[brfss22$Age_midpt]
brfss22$income_midpoint <- fct_recode(brfss22$INCOME3, 
                        "7500" = "Household income less than $10,000",
                        "12500" = "Less than $15,000 ($10,000 to less than $15,000)",
                        "17500" = "Less than $20,000 ($15,000 to less than $20,000) ",
                        "22500" = "Less than $25,000 ($20,000 to less than $25,000) ",
                        "30000" = "Less than $35,000 ($25,000 to less than $35,000) ",
                        "42500" = "Less than $50,000 ($35,000 to less than $50,000) ",
                        "62500" = "Less than $75,000 ($50,000 to less than $75,000)",
                        "87500" = "Less than $100,000 ($75,000 to less than $100,000)",
                        "125000" = "Less than $150,000 ($100,000 to less than $150,000)",
                        "175000" = "Less than $200,000 ($150,000 to less than $200,000)",
                        "210000" = "$200,000 or more",
                        NULL = "Dont know/Not sure",
                        NULL = "Refused")
brfss22$income_midpoint <- as.numeric(levels(brfss22$income_midpoint))[brfss22$income_midpoint]

brfss22$Educ_number <- fct_recode(brfss22$EDUCA, 
                                  "0" = "Never attended school or only kindergarten", 
                                  "4.5" = "Grades 1 through 8 (Elementary)",
                                  "10" = "Grades 9 through 11 (Some high school)",
                                  "12" = "Grade 12 or GED (High school graduate)",
                                  "14" = "College 1 year to 3 years (Some college or technical school)",
                                  "16" = "College 4 years or more (College graduate)",
                                  NULL = "Refused" )
brfss22$Educ_number <- as.numeric(levels(brfss22$Educ_number))[brfss22$Educ_number]


levels(brfss22$X_PRACE2)[7] <- "dont know not sure"

select1 <- !is.na(brfss22$MARIJAN1)

brfss_marijan <- subset(brfss22, select1 )


p_cannabis_age <- ggplot(data = brfss_marijan,
                       mapping = aes(x = Age_midpt,
                                     y = MARIJAN1))
p_cannabis_age + geom_smooth()

```

``` {r}
select2 <- !is.na(brfss22$MARIJAN1)
brfss_marijan <- subset(brfss22, select2 )


p_cannabis_income <- ggplot(data = brfss_marijan,
                       mapping = aes(x = income_midpoint,
                                     y = MARIJAN1))
p_cannabis_income + geom_smooth()
```

```{r}
model_2 <- lm(MARIJAN1 ~ Age_midpt + MARITAL + MSCODE + EDUCA , data = brfss_marijan)
summary(model_2)

model_3 <- lm(MARIJAN1 ~ Age_midpt + I(Age_midpt^2) + MARITAL + MSCODE + EDUCA, data = brfss_marijan)
summary(model_3)
```

```{r}
to_be_predicted_2 <- data.frame(Age_midpt = 25:55, MARITAL = "Married",
                          MSCODE = "in central city", EDUCA = "College 4 years or more (College graduate)")

to_be_predicted_2$yhat <- predict(model_2, newdata = to_be_predicted_2)

summary(to_be_predicted_2$yhat)
```

```{r}
summary
model_4 <- lm(MARIJAN1 ~ Age_midpt*(MARITAL + EDUCA) + I(Age_midpt^2)*(MARITAL + EDUCA) + MARITAL + MSCODE + EDUCA, data = brfss_marijan)
summary(model_4)
```
```{r}
anova(model_2, model_3, model_4)
```

```{r}
to_be_predicted_2$yhat3 <- predict(model_3, newdata = to_be_predicted_2)
to_be_predicted_2$yhat4 <- predict(model_4, newdata = to_be_predicted_2)


d_for_graphing <- data.frame(Age_midpt = 25:55, 
                             to_be_predicted_2$yhat,
                             to_be_predicted_2$yhat3,
                             to_be_predicted_2$yhat4)

p_predvals <- ggplot(d_for_graphing, aes(Age_midpt))
p_predvals + geom_line(aes(y = to_be_predicted_2.yhat)) + 
  geom_line(aes(y = to_be_predicted_2.yhat3), color = 'blue') +
  geom_line(aes(y = to_be_predicted_2.yhat4), color = 'red')
```

```{r}
quantile(brfss_marijan$MARIJAN1, probs = c(0.99,0.95,0.94,0.93,0.92,0.91,0.9))

brfss_marijan$MARIJAN_factor <- as.factor(brfss_marijan$MARIJAN1)
summary(brfss_marijan$MARIJAN_factor)
```

```{r}
brfss_marijan$Marijan_01 <- as.numeric(brfss_marijan$MARIJAN1 > 0)

model_5 <- lm(Marijan_01 ~ Age_midpt*(MARITAL + EDUCA) + I(Age_midpt^2)*(MARITAL + EDUCA) + MARITAL + MSCODE + EDUCA, data = brfss_marijan)
summary(model_5)
```

```{r}
anova(model_4,model_5)
```


Carson, I., Wu, W., Knopf, A., Crawford, C. A., & Zapolski, T. C. B. (2024). On the relationship between online heterosexist discrimination and mental health and substance use among lgbtq+ young adults. Archives of Sexual Behavior. 

It examines whether the effect of OHD is mediated by internalized heterosexism, online concealment, and acceptance concerns, and if social support moderates these relationships. The study employs Meyer’s minority stress theory (MST) as a framework for understanding these processes.

The data for this study were collected from 383 LGBTQ+ young adults aged 18–35, using a combination of an introductory psychology subject pool, two online crowdsourcing platforms, and community recruitment methods. Participants completed a questionnaire assessing experiences of OHD, online social support, online sexual orientation concealment, acceptance concerns, internalized heterosexism, psychological distress, and substance use (including alcohol, cannabis, and other drugs).

The study found that OHD was associated with increased psychological distress and cannabis use. Acceptance concerns and sexual orientation concealment mediated the relationship between OHD and psychological distress, while sexual orientation concealment also mediated the relationship between OHD and cannabis use. The study did not find evidence that online social support from LGBTQ+ peers moderated any of these relationships.