---
title: "exam2"
author: "Hanfei Dong"
date: "2024-04-18"
output: html_document
---
```{r}
load("D:/psy StatMethod/Household_Pulse_data_ph4c2.RData")
```

```{r}
library(tidyverse)
```

```{r}
Household_Pulse_data$AGE <- 2024 - Household_Pulse_data$TBIRTH_YEAR
```

```{r}
Household_Pulse_data$lonely <- NA
```

```{r}
Household_Pulse_data$lonely[Household_Pulse_data$AGE >= 15 & Household_Pulse_data$AGE <= 25] <- ifelse(runif(sum(Household_Pulse_data$AGE >= 15 & Household_Pulse_data$AGE <= 25)) < 0.3, 1, 0)
```

```{r}
group_summary <- Household_Pulse_data %>%
  group_by(AGE, MS) %>%
  summarise(
    estimate = mean(lonely, na.rm = TRUE),
    std_error = sd(lonely, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )
```

```{r}
print(group_summary)
```

```{r}
age_loneliness <- data.frame(
  age_group = c('[15,25]', '(25,35]', '(35,45]', '(45,55]', '(55,65]', '(65,75]', '(75,85]', '(85,95]'),
  not_lonely = c(1699, 7663, 10937, 9742, 11997, 11480, 3459, 329),
  lonely = c(569, 1478, 1658, 1319, 1204, 758, 179, 28)
)
```

```{r}
age_loneliness$prop_lonely <- age_loneliness$lonely / (age_loneliness$lonely + age_loneliness$not_lonely)
```

```{r}
age_loneliness$std_error <- sqrt((age_loneliness$prop_lonely * (1 - age_loneliness$prop_lonely)) / (age_loneliness$lonely + age_loneliness$not_lonely))
```

```{r}
test_result <- prop.test(x = c(age_loneliness$lonely[1], age_loneliness$lonely[2]),
                         n = c(age_loneliness$not_lonely[1] + age_loneliness$lonely[1],
                               age_loneliness$not_lonely[2] + age_loneliness$lonely[2]),
                         alternative = "two.sided", correct = FALSE)
```

```{r}
estimate <- test_result$estimate
conf_int <- test_result$conf.int
p_value <- test_result$p.value
```

```{r}
print(estimate)
print(conf_int)
print(p_value)
```

Question 1: The hypothesis test was aimed at comparing whether there was a significant difference in the proportion feeling lonely in the 15-25 and 25-35 age groups. The null hypothesis was that there is no difference in the proportion of loneliness in these two age groups. Based on the data provided, the estimated proportion of loneliness in the 15-25 age group was 25.08%, while the estimated proportion in the 25-35 age group was 16.17%. 95% confidence intervals indicated that the difference between these two proportions ranged from 6.98% to 10.86%. p-value of 3.81 x 10-23 was much lower than 0.05, which suggests that we have enough evidence to reject the null hypothesis. Therefore, a higher percentage of the 15-25 year old group reported loneliness than the 25-35 year old group.


```{r}
education_marital_status <- matrix(c(15022, 7103, 6017, 20927, 4617, 6425),
                                   nrow = 2,
                                   dimnames = list(c("not 4yr degree", "4yr or more"),
                                                   c("married", "divorced_or_separated", "never_married")))
```

```{r}
chi_squared_test <- chisq.test(education_marital_status)
```

```{r}
chi_squared_test
```

Question 2: The null hypothesis is that among married, divorced/widowed/separated, and unmarried people, education level is independently and unrelated to the frequency of reports of loneliness.
Based on the results of the Pearson chi-square test, we obtained a very high chi-square statistic value of 10314 with a degree of freedom of 2 and a p-value of less than 2.2 x 10-16. This extremely small p-value suggests that there is a very strong correlation between level of education and frequency of loneliness reports among married, divorced/widowed/separated, and unmarried populations. We therefore reject the null hypothesis. Therefore, we have statistical evidence to support the idea that education level and marital status are correlated with each other in terms of their effects on loneliness.


```{r}
Household_Pulse_data <- Household_Pulse_data %>%
  mutate(AGE = as.numeric(AGE), 
         )          
```

```{r}
linear_model <- lm(lonely ~ AGE + MS + EEDUC, data = Household_Pulse_data)
```

```{r}
summary(linear_model)
```

```{r}
anova_model <- anova(linear_model)
anova_model
```

Question 3:
I chose age, marital status and education level as predictor variables. I chose these variables because they have often been shown in social science research to be related to an individual's mental health and social connectedness. Age is an important factor because feelings of loneliness may change at different life stages; younger people may feel lonely due to changes in their social networks, while older people may feel lonely due to the loss of a partner or a change in social roles. Marital status is also included as a variable because the social support provided by marriage or partnership is often considered a protective factor against loneliness. On the other hand, divorce, widowhood or separation may increase loneliness. Educational level may reflect socioeconomic status, and higher levels of education may be associated with larger social networks and better health, which may influence reports of loneliness.

In the present model, age and education level did not significantly explain the variance in loneliness. Marital status was the only factor that contained statistically significant predictor variables. In particular, married, separated, and unmarried individuals were associated with lower reports of loneliness.


```{r}
logit_model <- glm(lonely ~ AGE + MS + EEDUC, family = binomial, data = Household_Pulse_data)
```

```{r}
summary(logit_model)
```

Question 4: In logistic regression analyses of loneliness, married status significantly reduced the probability of reporting loneliness, while the categories of age and most levels of education were not statistically significant. This is consistent with some of the findings in the linear model, but the logistic regression more clearly reveals the significant protective effect of being married on reducing loneliness.

```{r}
library(rpart)
```

```{r}
tree_model <- rpart(lonely ~ AGE + MS + EEDUC, 
                    data = Household_Pulse_data, 
                    method = "class",
                    control = rpart.control(minsplit = 20, cp = 0.001))
```

```{r}
print(tree_model)
plot(tree_model)
text(tree_model, use.n = TRUE)
```
Question 5: The decision tree model revealed marital status as the most important predictor of loneliness.

